\documentclass[11pt,onecolumn]{article} 
\usepackage{latex8}
\bibliographystyle{latex8}
\usepackage{times}



\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Middleware Solutions for the Internet of Things}


% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{
Chinwei ``Vic'' Hu\\
{\small \textit{Department of Electrical and Computer Engineering} }\\
{\small \textit{The University of Texas at Austin}}
}


% make the title area
\maketitle


\begin{abstract}
The abstract is to be in fully-justified italicized text as it is here, below the author information. Use the word ⤽Abstract⤝ as the title, in 12-point Times New Roman, boldface type, centered relative to the column, initially capitalized. The abstract is to be in 11-point, single-spaced type, and may be up to 3 in. (18 picas or 7.62 cm) long. Leave two blank lines after the abstract, then begin the main text. All manuscripts must be in English. All text material for 6-by-9-inch proceedings will be formatted in a single column per page.
\end{abstract}



\Section{Introduction}


%\medskip
%\noindent
\Section{References}
List and number all bibliographical references in 9-point Times New Roman, single-spaced with 10-point interlining spacing, at the end of your paper. When referenced in the text, enclose the citation number in square brackets~\cite{IEEEhowto:kopka}. Where appropriate, include the name(s) of editors of referenced books.

% use section* for acknowledgement
\section*{Acknowledgment}
The authors would like to thank...
more thanks here

\begin{thebibliography}{1}
\small
\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

\end{document}

